---
title: "Heart Disease Analysis"
author: Oscar Monroy & Santiago Rodriguez
output: pdf_document
---
#Logistic  Regression
=====================

Let's load our data and count the duplicated responses. Note the survey responses
were not given a unique identifier, which leads to a lot of duplicate entries.
```{r}
hd <- read.csv("heart_2020_cleaned.csv")
attach(hd)

summary(hd)
sum(duplicated(hd))
```

For some reason the 'Yes' and 'No' replies in the data were not being understood 
very well  by R, so we converted $HeartDisease$ into a binary vector.
```{r}
library(dplyr)
hd2 <- hd %>% mutate(HeartDisease = ifelse(HeartDisease == 'Yes', 1, 0))
y <- hd2$HeartDisease
```

Now let's break up the data into training and test sets. Here we used 60% of 
the data as our training set.
```{r}
set.seed(1)

# Create training and test sets.
train <- sample(1:nrow(hd2), 0.6*nrow(hd2))
test <- (-train)

y.test <- y[test]
```

Now we apply Logistic Regression to the training set and then attempt to predict
the individuals with heart disease. We use every other variable as a predictor.

```{r}

#Apply logistic regression to training set.
model = glm(HeartDisease ~ ., data = hd2[train, ], family = binomial)
summary(model)

# Predict the responders that are diagnosed with heart disease.
model.pred = predict(model, data = hd2[test, ], type = 'response')
vec = rep(0, length(y))
vec[model.pred >= 0.5] = 1
```
Now let's check how well Logistic Regression predicted  $HeartDisease$
```{r}
mean(vec == y)
prop.table(table(vec, y))
```
Notice that our model did very poorly at detecting which individuals said they
had heart disease at some point.
